A generic and fast C++ optimization framework

### 2017-10-22 paper.tex
Slight change in phrasing, Section7

Unfortunately, template metaprogramming can result in some very lengthy error
messages.  Therefore, we must be careful to ensure that a user is able to easily
debug a problem when they implement an objective function or gradient.  To
provide good error message output, we can use C++'s template metaprogramming
support to determine what methods a type has available.  Similarly, we can also
use static compile-time constants to denote the methods that are required by a
specific optimizer.  This is implemented via SFINAE
\cite{Vandevoorde2002sfinae}.  A {\tt static\_assert()} is raised when a given
objective function does not have the required methods for a given optimizer.

>>>>

Unfortunately, template metaprogramming can result in some very lengthy error
messages.  Therefore, we must be careful to ensure that a user is able to easily
debug a problem when they implement an objective function or gradient.  To
 improve error message output, we can use C++'s template metaprogramming
support to determine what methods a type has available.  Similarly, we can also
use static compile-time constants to denote the methods that are required by a
specific optimizer.  This is implemented via SFINAE
\cite{Vandevoorde2002sfinae}.  A {\tt static\_assert()} is raised when a given
objective function does not implement the methods required by the optimizer used.
